Sketch of DP - Bayesian Inference

### 2018-07-16 main-sketch.tex
fix expression in section 1

  \Pr(\dataobs | \theta)\equiv \theta^{a}(1-\theta)^{n-a}

@@

where $a=\displaystyle\sum_{i=1}^{n}\mathrm{x_i}$.

@@

  \Pr(\theta|\dataobs)=\betad(\alpha+a,\beta+n-a)

@@

  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a\in\datauni}\alpha_{a}^{z_a}

@@

where $z_a=\displaystyle\sum_{i=1}^{n}\iverson{x_i=a}$, where in $\iverson{\cdot}$ we use

@@

  \Pr(\vtheta|\dataobs)=\dirichlet(\vtheta+\mathbf{z})

@@

\section{Baseline Approach - Laplace Mechanism}
\label{sec_lap}
Our baseline approach come from the algorithm designed by \citet{zhang2016differential} that adding Laplace noise (\citet{dwork2014algorithmic}) to posterior parameters to preserve privacy. They perturbed $\betad$ distribution updates and truncated at $0$ to rule out invalid $\betad$ parameters to get the protected posteriors. Here we also extend their algorithm to the case of $m$ dimensional Dirichlet distributions, where we add $(m-1)$ i.i.d. Laplace noises $\{Lap_1 , Lap_2, \cdots, Lap_{m-1} \}$ and truncate in the same way. 
%where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. 
The private posterior then will be $\dirichlet(\alpha_1 + z_1 + Lap_1, \alpha_2 + z_2 + Lap_2, \cdots, \alpha_m + n - (Lap_1 + \cdots + Lap_{m-1}))$.

>>>>

  \Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}

@@

where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}\mathrm{x_i}$.

@@

  \Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)

@@

  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i}

@@

where $\Delta \alpha_i=\displaystyle\sum_{i=1}^{n}\iverson{x_i=a_i}$, where in $\iverson{\cdot}$ we use

@@

  \Pr(\vtheta|\dataobs)=\dirichlet(\valpha+\Delta \valpha)

@@

\section{Baseline Approach - Laplace Mechanism}
\label{sec_lap}
Our baseline approach come from the algorithm designed by \citet{zhang2016differential} that adding Laplace noise (\citet{dwork2014algorithmic}) to posterior parameters to preserve privacy. They perturbed $\betad$ distribution updates and truncated at $0$ to rule out invalid $\betad$ parameters to get the protected posteriors. Here we also extend their algorithm to the case of $m$ dimensional Dirichlet distributions, where we add $(m-1)$ i.i.d. Laplace noises $\{Lap_1 , Lap_2, \cdots, Lap_{m-1} \}$ and truncate in the same way. 
%where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. 
The private posterior then will be $\dirichlet(\alpha_1 + \Delta \alpha_1 + Lap_1, \alpha_2 + \Delta \alpha_2 + Lap_2, \cdots, \alpha_m + n - (Lap_1 + \cdots + Lap_{m-1}))$.
